GPU-Accelerated Parallelization of Edge-Based Motion Detection Algorithms with the NVIDIA CUDA Framework

### 2015-12-06 documents/paper/paper.tex
Add some speedup results

\subsection{GPU Computation and the NVIDIA CUDA Framework}
Formally, NVIDIA CUDA is a parallel computing platform and programming model that exposes familiar C-based APIs for parallelized computations. CUDA is NVIDIA's platform for general-purpose computing on graphics processing units (commonly, GPGPU or GP$^2$U), or the use of a GPU for computations traditionally handled by the CPU. Generally, GPGPU is used to exploit the improved multithreaded performance and raw floating-point computational ability of GPUs over CPUs. For example, on modern hardware, an NVIDIA GeForce GTX 970 (1664 CUDA cores) exhibits peak single-precision floating point performance of nearly 3500 GFLOPS (floating-point operations per second), while an Intel Core i7 4790K (8C, 16T) achieves 100 GFLOPS. Our goal is to demonstrate the performance of GPU computing by solving a handful of existing problems in computer vision with CUDA: namely, edge detection and motion detection.

@@

\section{GPU Speedup Results}
Placeholder text

>>>>

\subsection{GPU Computation and the NVIDIA CUDA Framework}
Formally, NVIDIA CUDA is a parallel computing platform and programming model that exposes familiar C-based APIs for parallelized computations. CUDA is NVIDIA's platform for general-purpose computing on graphics processing units (commonly, GPGPU or GP$^2$U), or the use of a GPU for computations traditionally handled by the CPU. Generally, GPGPU is used to exploit the improved multithreaded performance and raw floating-point computational ability of GPUs over CPUs. For example, on modern hardware, an NVIDIA GeForce GTX 970 (1664 CUDA cores) exhibits peak single-precision floating point performance of nearly 3500 GFLOPS (floating-point operations per second), while an Intel Core i7 4790K (4C, 8T) achieves 100 GFLOPS. Our goal is to demonstrate the performance of GPU computing by solving a handful of existing problems in computer vision with CUDA: namely, edge detection and motion detection.

@@

\section{GPU Speedup Results}
Our code for separable convolution, computation of the image's gradient magnitude and angle, non-maximum suppression and selective thresholding, and computation of the thresholded difference and spatial difference density matrices has both serial CPU and parallel CUDA implementations. Here, we present speedup results for each of these procedures on various image sizes obtained on a system with the following hardware:
\begin{itemize}
	\item Intel Core i7 4790K @ 4.7 GHz (4C, 8T)
	\item 16 GB of DDR3 memory @ 1600 MHz
	\item NVIDIA GeForce GTX 750 (512 CUDA cores, 1437 MHz core clock, 6500 MHz memory clock, 2 GB video memory)
\end{itemize}

\subsection{Separable convolution}
The below results were obtained by convolving the same image, resized to various image dimensions, with a separated Gaussian filter of kernel size $k = 3$.
\begin{table}[H]
	\small
	\centering
	\caption{Speedup of Separable Convolution}
	\label{separable-convolution-speedup}
	\begin{tabular}{llllll}
	 Image dimensions & CPU time (s) & GPU time (s) & Speedup \\
	 $100 \times 100$ & $0.000191$ & $0.054855$ & $0.003482$ \\
	 $500 \times 500$ & $0.004748$ & $0.002728$ & $1.740469$ \\
	 $1000 \times 1000$ & $0.018850$ & $0.008431$ & $2.235796$ \\
	 $2000 \times 2000$ & $0.074475$ & $0.034503$ & $2.158508$ \\
	 $3000 \times 3000$ & $0.167459$ & $0.072181$ & $2.319987$ \\
	 $4000 \times 4000$ & $0.299840$ & $0.136641$ & $2.194363$ \\
	 $5000 \times 5000$ & $0.465225$ & $0.194512$ & $2.391755$ \\
	 $6000 \times 6000$ & $0.673266$ & $0.276730$ & $2.432935$ \\
	 $7500 \times 7500$ & $1.052294$ & $0.439262$ & $2.395595$ \\
	\end{tabular}
\end{table}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.45\textwidth]{separable_convolution_speedup_graph.jpg}
	\caption{Visualization of separable convolution speedup versus pixel count}
    \label{separable-convolution-speedup-graph}
\end{figure}

\subsection{Non-maximum suppression and selective thresholding}

\subsection{Thresholded spatial difference density matrix}
